---
title: "MarkdownReport"
author: "Sara Romagnoli"
date: "2024-01-11"
output: html_document
---

# My first markdown document!

Here you can add text if you want

To acces and close the code we use '''

In this case we obtain a result:
```{r, eval=T}
2+3
```

in this case not:
```{r, eval=F}
2+3
```

Using proper packages; the imageRy package as we nuilt at Alma Mater for learningremote sensing:
```{r, eval=T}
library(imageRy)
```

Let's import some data, starting with a list of data:
```{r, eval=T}
im.list()
```

Importing Mato Grosso area image:
```{r, eval=T}
Mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

In order to get info on the image, just type the name of the object:
```{r, eval=T}
Mato1992
```

Plotting the Mato Grosso area with the NIR on top of the green component of the RGB 
```{r, eval=T}
im.plotRGB(Mato1992, r= 2, g=1, b=3)
```

Importing Mato Grosso area image without warnings:
```{r, eval=T, warning=F}
Mato1992 <- im.import("matogrosso_l5_1992219_lrg.jpg")
```

Plotting several images all together:
```{r, eval=T}
par(mfrow=c(2,2))
im.plotRGB(Mato1992, r= 1, g=2, b=3)
im.plotRGB(Mato1992, r= 2, g=1, b=3)
im.plotRGB(Mato1992, r= 3, g=2, b=1)
im.plotRGB(Mato1992, r= 1, g=3, b=1)
```

Calculating spectral indeces:
```{r, eval=T}
library(terra)
library(viridis)
DVI <- Mato1992[[1]]-Mato1992[[2]]
viridisc <- colorRampPalette(viridis(7))(255)
plot(DVI, col=viridisc)
```

```{r, eval=T, warning=F}
sd5 <- focal(Maro1992[[1]], matrix(1/25, 5, 5), fun+sd)
plot(sd5, col=viridisc)
```
